Constant-round Blind Classical Verification of Quantum Sampling

### 2020-04-15 qpip0.tex
Change epsilon font

	Inputs:
	\begin{itemize}
		\item Security parameter $1^\lambda$ where $\lambda\in\bbN$
		\item Error parameter $\varepsilon\in(0, 1)$
		\item Classical input $x\in\zo^n$ to the $\SampBQP$ instance
	\end{itemize}

@@

\begin{lemma}[binding property of $\PiNaive$]
\label{lem:naive-qpip0-binding}
	Let $\PNaiveStar$ be a cheating $\BQP$ prover for $\PiNaive$ and $\lambda$ be the security parameter.
	Under the QLWE assumption, if $\PNaiveStar$ passes the testing round with probability $1-\negl(\lambda)$,
	\Ethan{Wrong assumption. The ``perfect prover" notion here is generalized and allows giving up.}
	then the verifier's output in the Hadamard round is $(\varepsilon+\negl(\lambda))$-computationally indistinguishable from $(d, z_{ideal})$.
\end{lemma}

\begin{proof}
	\Ethan{TODO this is currently wrong and I'm not sure how to fix it.
	The version before this which had subnormalized states seems strange too.
	The correct proof should involve an alternative prover strategy that ``fixes" the abort case
	by re-running with perfect prover strategy,
	in order to connect the dots with \Cref{lem:urmila-binding}}
	By \Cref{lem:urmila-binding},
	there exist some $\rho$ such that
	$v\approx_{c,\negl(\lambda)}M_{XZ}(\rho,h)$.
	Let $\cVVer$ be the verification operation in \stepref{qpip1-verify} of $\PiSamp$.
	Since $\cVVer$ is efficient, we have
	$(d,z)\approx_{c, \negl(\lambda)}\cVVer(M_{XZ}(\rho, h))$.
	\Ethan{There were some shenanigans involving subnormalized states for which I'm not quite sure what's going on.}
	By \Cref{QPIP1thm}, for all $\rho$, 
	$\cVVer(M_{XZ}(\rho, h))\approx_{c, \varepsilon}(d, z_{ideal})$.
	So we conclude that
	$(d, z)\approx_{c, \varepsilon+\negl(\lambda)}(d, z_{ideal})$.

@@

Inputs:
	\begin{itemize}
		\item Security parameter $1^\lambda$ for $\lambda\in\bbN$.
		\item Accuracy paramter $1^{1/\varepsilon}$ for the $\SampBQP$ instance
		\item Input $x\in\zo^{\poly(\lambda)}$ for the $\SampBQP$ instance
	\end{itemize}

Ingrediant: Let $m=O(1/\varepsilon^2)$ be the number of parallel repetitions to run.

Protocol:
\begin{enumerate}
	\item The verifier generates $m$ independently copies of basis choices $\vec{h}=(h_1,\ldots,h_m)$ as in \stepref{naive1} of $\PiNaive$
	\item The prover prepares $\rho^{\otimes m}$ on inputs $1^\lambda$, $1^{1/\varepsilon}$, and $x$. Each copy of $\rho$ is prepared as in \stepref{naive2} of $\PiNaive$
	\item The verifier generates $m$ key pairs for $\PiMeasure$, $\vec{pk}=(pk_1,\ldots,pk_m)$ and $\vec{sk}=(sk_1,\ldots,sk_m)$, on inputs $1^\lambda$ and $\vec{h}$, as in \stepref{measure1} of $\PiMeasure$.
		It sends $\vec{pk}$ to the prover.
	\item The prover generates $\vec{y}=(y_1,\ldots,y_m)$ and $\sigma$ on inputs $\vec{pk}$ and $\rho^{\otimes m}$ as in \stepref{measure2} of $\PiMeasure$.
		It sends $\vec{y}$ to the verifier.
	\item The verifier samples $r\xleftarrow{\$}[m]$ which is the copy to run Hadamard round for.
		For $1\leq i\leq m$, if $i\ne r$ then set $c_i\leftarrow 0$, else set $c_i\leftarrow 1$.
		It sends $\vec{c}=(c_1,\ldots,c_m)$ to the prover.
	\item The prover generates $\vec{a}$ on inputs $\vec{pk}, \vec{c}, \sigma$ as in \stepref{measure4} of $\PiMeasure$, and sends it back to the verifier.
	\item \label{step:multi-testing}
		The verifier computes the outcome for each round as in \stepref{output} of $\PiMeasure$.
		If any of the testing round copies are rejected, the verifier outputs $(\Rej, \bot)$.
		Else, it outputs the result from the Hadamard round copy.
\end{enumerate}
\end{protocol}

@@

\Ethan{This proof currently only shows $O(\varepsilon)$ accuracy, which doesn't perfectly match up with the definition. Hopefully doesn't matter way too much though?}

>>>>

	Inputs:
	\begin{itemize}
		\item Security parameter $1^\lambda$ where $\lambda\in\bbN$
		\item Error parameter $\eps\in(0, 1)$
		\item Classical input $x\in\zo^n$ to the $\SampBQP$ instance
	\end{itemize}

@@

\begin{lemma}[binding property of $\PiNaive$]
\label{lem:naive-qpip0-binding}
	Let $\PNaiveStar$ be a cheating $\BQP$ prover for $\PiNaive$ and $\lambda$ be the security parameter.
	Under the QLWE assumption, if $\PNaiveStar$ passes the testing round with probability $1-\negl(\lambda)$,
	\Ethan{Wrong assumption. The ``perfect prover" notion here is generalized and allows giving up.}
	then the verifier's output in the Hadamard round is $(\eps+\negl(\lambda))$-computationally indistinguishable from $(d, z_{ideal})$.
\end{lemma}

\begin{proof}
	\Ethan{TODO this is currently wrong and I'm not sure how to fix it.
	The version before this which had subnormalized states seems strange too.
	The correct proof should involve an alternative prover strategy that ``fixes" the abort case
	by re-running with perfect prover strategy,
	in order to connect the dots with \Cref{lem:urmila-binding}}
	By \Cref{lem:urmila-binding},
	there exist some $\rho$ such that
	$v\approx_{c,\negl(\lambda)}M_{XZ}(\rho,h)$.
	Let $\cVVer$ be the verification operation in \stepref{qpip1-verify} of $\PiSamp$.
	Since $\cVVer$ is efficient, we have
	$(d,z)\approx_{c, \negl(\lambda)}\cVVer(M_{XZ}(\rho, h))$.
	\Ethan{There were some shenanigans involving subnormalized states for which I'm not quite sure what's going on.}
	By \Cref{QPIP1thm}, for all $\rho$, 
	$\cVVer(M_{XZ}(\rho, h))\approx_{c, \eps}(d, z_{ideal})$.
	So we conclude that
	$(d, z)\approx_{c, \eps+\negl(\lambda)}(d, z_{ideal})$.

@@

Inputs:
	\begin{itemize}
		\item Security parameter $1^\lambda$ for $\lambda\in\bbN$.
		\item Accuracy paramter $1^{1/\eps}$ for the $\SampBQP$ instance
		\item Input $x\in\zo^{\poly(\lambda)}$ for the $\SampBQP$ instance
	\end{itemize}

Ingrediant: Let $m=O(1/\eps^2)$ be the number of parallel repetitions to run.

Protocol:
\begin{enumerate}
	\item The verifier generates $m$ independently copies of basis choices $\vec{h}=(h_1,\ldots,h_m)$ as in \stepref{naive1} of $\PiNaive$
	\item The prover prepares $\rho^{\otimes m}$ on inputs $1^\lambda$, $1^{1/\eps}$, and $x$. Each copy of $\rho$ is prepared as in \stepref{naive2} of $\PiNaive$
	\item The verifier generates $m$ key pairs for $\PiMeasure$, $\vec{pk}=(pk_1,\ldots,pk_m)$ and $\vec{sk}=(sk_1,\ldots,sk_m)$, on inputs $1^\lambda$ and $\vec{h}$, as in \stepref{measure1} of $\PiMeasure$.
		It sends $\vec{pk}$ to the prover.
	\item The prover generates $\vec{y}=(y_1,\ldots,y_m)$ and $\sigma$ on inputs $\vec{pk}$ and $\rho^{\otimes m}$ as in \stepref{measure2} of $\PiMeasure$.
		It sends $\vec{y}$ to the verifier.
	\item The verifier samples $r\xleftarrow{\$}[m]$ which is the copy to run Hadamard round for.
		For $1\leq i\leq m$, if $i\ne r$ then set $c_i\leftarrow 0$, else set $c_i\leftarrow 1$.
		It sends $\vec{c}=(c_1,\ldots,c_m)$ to the prover.
	\item The prover generates $\vec{a}$ on inputs $\vec{pk}, \vec{c}, \sigma$ as in \stepref{measure4} of $\PiMeasure$, and sends it back to the verifier.
	\item \label{step:multi-testing}
		The verifier computes the outcome for each round as in \stepref{output} of $\PiMeasure$.
		If any of the testing round copies are rejected, the verifier outputs $(\Rej, \bot)$.
		Else, it outputs the result from the Hadamard round copy.
\end{enumerate}
\end{protocol}

@@

\Ethan{This proof currently only shows $O(\eps)$ accuracy, which doesn't perfectly match up with the definition. Hopefully doesn't matter way too much though?}
